Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-12-30 submission/NatCom_cv_models.tex
images updated
getting appendix in place

    \subfigure[ ResNet, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet-1K_logpnorm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \caption{Comparison of Average $\alpha$-Norm quality metric versus reported Top1 test accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. 
             \michael{FROM V1: Symbols and text are way to small on these and other figures; axes/ticks way too small; need different symbols, not just red versus green; etc.}
            }
    \label{fig:cv2-accuracy}
\end{figure}

@@

Informally, one would expect a DNN model to perform well when it facilitates the propagation of information/features across layers.
In the absence of training/test data, one might hypothesize that this flow of information leaves empirical signatures on weight matrices, and that we can quantify this by measuring the PL properties of weight matrices.
In this case, smaller $\alpha$ values correspond to layers in which information correlations between data across multiple scales are better captured~\cite{MM18_TR,SornetteBook}.
This leads to the hypothesis that small $\alpha$ values that are stable across multiple layers enable better correlation flow through the network.
This is similar to recent work on the information bottleneck~\cite{ST17_TR}, except that here we work in an entirely unsupervised setting.

>>>>

    \subfigure[ ResNet, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, Log $\alpha$-Norm ]{
        \includegraphics[width=4.9cm]{img/ResNet-1K_log_alpha_norm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \caption{Comparison of Average $\alpha$-Norm quality metric versus reported Top1 test accuracy for the ResNet and ResNet-1K pretrained (pyTorch) models. 
             \michael{FROM V1: Symbols and text are way to small on these and other figures; axes/ticks way too small; need different symbols, not just red versus green; etc.}
            }
    \label{fig:cv2-accuracy}
\end{figure}

@@

Informally, one would expect a DNN model to perform well when it facilitates the propagation of information/features across layers.
In the absence of training/test data, one might hypothesize that this flow of information leaves empirical signatures on weight matrices, and that we can quantify this by measuring the PL properties of weight matrices.
In this case, smaller $\alpha$ values correspond to layers in which information correlations between data across multiple scales are better captured~\cite{MM18_TR,SornetteBook}.
This leads to the hypothesis that small $\alpha$ values that are stable across multiple layers enable better correlation flow through the network.
This is similar to recent work on the information bottleneck~\cite{TZ15,ST17_TR}, except that here we work in an entirely unsupervised setting.

### 2020-12-30 submission/NatCom_overall_approach.tex
getting appendix in place

Based on this, in this paper, we introduce and evaluate the $\alpha$-Shatten Norm metric,
\begin{equation}
\label{eqn:sum_log_alpha_norm_alpha}
\sum\nolimits_l \log \Vert\mathbf{X}_l\Vert_{\alpha_l}^{\alpha_l} 
=
\sum\nolimits_l \alpha_l \log \Vert\mathbf{X}_l\Vert_{\alpha_l} .
\end{equation}
For the $\alpha$-Shatten Norm metric, $\alpha_l$ varies from layer to layer, and so in Eqn.~(\ref{eqn:sum_log_alpha_norm_alpha}) it cannot be taken out of the sum.
For small $\alpha$, the Weighted Alpha metric approximates the Log $\alpha$-Shatten norm, as can be shown with a statistical mechanics and random matrix theory derivation \cite{MM20_unpub_work}; and the Weighted Alpha and $\alpha$-Shatten norm metrics often behave like an improved, weighted average Log Spectral Norm.

>>>>

Based on this, in this paper, we introduce and evaluate the $\alpha$-Shatten Norm metric,
\begin{equation}
\label{eqn:sum_log_alpha_norm_alpha}
\sum\nolimits_l \log \Vert\mathbf{X}_l\Vert_{\alpha_l}^{\alpha_l} 
=
\sum\nolimits_l \alpha_l \log \Vert\mathbf{X}_l\Vert_{\alpha_l} .
\end{equation}
For the $\alpha$-Shatten Norm metric, $\alpha_l$ varies from layer to layer, and so in Eqn.~(\ref{eqn:sum_log_alpha_norm_alpha}) it cannot be taken out of the sum.
For small $\alpha$, the Weighted Alpha metric approximates the Log $\alpha$-Shatten norm, as can be shown with a statistical mechanics and random matrix theory derivation;
%% \cite{MM20_unpub_work}; 
and the Weighted Alpha and $\alpha$-Shatten norm metrics often behave like an improved, weighted average Log Spectral Norm.
